---
title: "Introduction Julia"
subtitle: "Data Science and Machine Learning"
author: "Emmanuel Rialland"
date: "April, 29th 2020"
output:
  xaringan::moon_reader:
    chakra: libs/remark-latest.min.js
    lib_dir: libs
    yolo: true
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
#xaringan::summon_remark()
options(htmltools.dir.version = FALSE)
options(servr.daemon = TRUE)
```


```{r, include=FALSE}
JuliaCall::julia_markdown_setup(JULIA_HOME = "/opt/julia/bin", notebook = TRUE)
```


--- 

# Plan for today

- What is Julia and short comparison

--

- Data Science - COVID 19 as an example

--

- Machine Learning - the Julia Flux.jl library

---
class: inverse, center, middle

# What is Julia?

---

---
class: inverse, center, middle

# Data science with COVD19 

---

---
class: inverse, center, middle

# The `Flux.jl` machine learning library

---

# Is it really quick?

Nice picture

***

---

Code:

```{julia}
A = B = [1 2; 3 4]
2 * A + 3 * B

@show 2 * A + 3 * B
#>> 2A + 3B = [5 10; 15 20]
```


```{julia}
Γ = Λ = [1 2; 3 4]
2 * Γ + 3 * Λ

@show 2 * Γ + 3 * Λ
#>> 2Γ + 3Λ = [5 10; 15 20]
```


```{julia}
length(methods(*))
#>> 368
```


```{julia}
@show first(methods(*))
#>> first(methods(*)) = *(x::Bool, z::Complex{Bool}) in Base at complex.jl:290
```


```{julia}
function add(x::Int64, y::Int64)::Int64
  return x + y
end

function add(x::Float64, y::Float64)::Float64
  return x + 2.0 * y
end

function add(x::Any, y::Any)::Any
  return x + y
end
```


```
@code_llvm add(1.0, 2.0)


# define double @julia_add_18854(double, double) {
# top:
# ; ┌ @ float.jl:405 within `*'
#    %2 = fmul double %1, 2.000000e+00
# ; └
# ; ┌ @ float.jl:401 within `+'
#    %3 = fadd double %2, %0
# ; └
#   ret double %3
# }


@code_native add(1.0, 2.0)

# ; ┌ @ scratchpad.jl:27 within `add'
# ; │┌ @ scratchpad.jl:27 within `*'
#     vaddsd  %xmm1, %xmm1, %xmm1
# ; │└
# ; │┌ @ float.jl:401 within `+'
#     vaddsd  %xmm0, %xmm1, %xmm0
# ; │└
#     retq
#     nopl    (%rax)
# ; └


@code_llvm add(1, 2)
# define i64 @julia_add_18857(i64, i64) {
# top:
# ; ┌ @ int.jl:53 within `+'
#    %2 = add i64 %1, %0
# ; └
#   ret i64 %2
# }

@code_native add(1, 2)
# ; ┌ @ scratchpad.jl:23 within `add'
# ; │┌ @ scratchpad.jl:23 within `+'
#     leaq    (%rdi,%rsi), %rax
# ; │└
#     retq
#     nopw    %cs:(%rax,%rax)
#     nop
# ; └
```


$$
\frac{dx}{dt} = \sigma (y - x) \\
\frac{dy}{dt} = x (\rho - z) - y \\
\frac{dz}{dt} = x y - \beta z
$$



---
class: center, middle

# Thanks and links

Written in **RStudio** in [R Markdown](https://rmarkdown.rstudio.com)

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).

(C) Emmanuel Rialland - [Emmanuel-R8.github.io](https://Emmanuel-R8.github.io/) & [www.linkedin.com/in/emmanuelrialland](https://www.linkedin.com/in/emmanuelrialland)


